---
title: "Project 2"
author: "520523472, 520048207, 520220674, 520448692, 510450920, 500499069"
subtitle: "What Lifestyle Factors affect Hours of Sleep?"
date: "University of Sydney | 12th April 2022"
output:
  html_document:
    fig_caption: yes
    number_sections: yes
    self_contained: yes
    theme: flatly
    toc: true
    toc_depth: 3
    toc_float: true
    code_folding: hide
---

# Executive Summary
•	Clear & Interesting
•	Main Insights 💡✨
•	Type of Data

# Initial Data Analysis (IDA)
```{r}
setwd("/Users/itme/Desktop/DATA1001/Project 2")
survey=read.csv("SurveyResponses.csv")

str(survey)
```

```{r}
#Load 'tidyverse' package
library(tidyverse)

#DATA CLEANING
surveyC = survey %>%
  filter(survey$Shots %in% c(1:100) & survey$Sleep %in% c(0:24))

# Exclude intentionally silly responses
surveyC$Shots=as.numeric(surveyC$Shots)
# Change the 'Like 30-40hrs' response to N/A
surveyC$Work=as.numeric(surveyC$Work)

# Replace 'None' in Naps with 0
Naps=replace(surveyC$Naps,surveyC$Naps=="None","0")
surveyC$Naps=as.numeric(Naps)

# Change variable types: chr to num
surveyC$Shots=as.numeric(surveyC$Shots)
surveyC$Sleep=as.numeric(surveyC$Sleep)
surveyC$Naps=as.numeric(surveyC$Naps)
surveyC$Shots=as.numeric(surveyC$Shots)
surveyC$Screen=as.numeric(surveyC$Screen)
surveyC$Milk=as.factor(surveyC$Milk)
surveyC$Wake=as.factor(surveyC$Wake)
surveyC$Age=as.factor(surveyC$Age)
surveyC$Sex=as.factor(surveyC$Sex)
surveyC$Exercise=as.factor(surveyC$Exercise)

# Order Wake up times in order:
WakeO=factor(survey$Wake, levels=c("2:00","4:30", "4:45","5:00","5:30","6:00","6:30","6:45","7:00","7:10","7:15","7:20","7:35","8:00","8:30","9:00","9:30","10:00","10:30","11:00","11:30","12:00"))
```

## Cleaned Data
```{r}
# View the Raw Data (to check everything is A-okay)
view(surveyC)
```


### Source
* [where the data came from]

### Structure
[size & type of variables, incl. reclassification]
* There are 152 individual responses exploring 11 variables.

### Limitations
* [careful: ‘Statistical Thinking’]

### Assumptions
* [a priori ideas]

### Data Cleaning
[changes from original format]




# Research Question/s
## Does Caffeine strongly influence Hours of Sleep differently for Fe/males? 
```{r}
# SCATTERPLOT of CAFFEINE & SLEEP: 
P=ggplot(surveyC, aes(Shots/7,Sleep,fill=Sex)) +geom_point(size=3, pch=21) +labs(x="Caffeine (shots)", y="Sleep (hours)", title="Relationship between Caffeine and Hours of Sleep") +scale_fill_manual(values=c("magenta","cornflowerblue"))
P
```

### Correlation Coefficients (2x)

```{r}
#Create subsets for Fe/male
Fem_surveyC=subset(surveyC, surveyC$Sex =="Female")
Male_surveyC=subset(surveyC, surveyC$Sex=="Male")
```

* Female
```{r}
Fem_cor=cor(Fem_surveyC$Sleep,Fem_surveyC$Shots)
Fem_cor
```
* Male
```{r}
Male_cor=cor(Male_surveyC$Sleep,Male_surveyC$Shots)
Male_cor
```

### Regression Lines (2x)
* Female
```{r}
Lf=lm(Fem_surveyC$Sleep~Fem_surveyC$Shots)
Lf$coeff
lm(Sleep~Shots, Fem_surveyC)
```
* Male
```{r}
Lm=lm(Male_surveyC$Sleep~Male_surveyC$Shots)
Lm$coeff
lm(Sleep~Shots, Male_surveyC)
```
### Residual Plots (2x)
```{r}
par(mfrow=c(1,2))
plot(Fem_surveyC$Shots, Lf$residuals, xlab="Caffeine (shots)", ylab="Residuals") + abline (h=0,col="magenta")
plot(Male_surveyC$Shots, Lm$residuals, xlab="Caffeine (shots)", ylab="Residuals") + abline (h=0,col="cornflowerblue")
```


### Regression Lines on Scatterplot
```{r}
R=ggplot(surveyC, aes(Shots/7,Sleep,fill=Sex)) +geom_point(size=3, pch=21) +labs(x="Caffeine (shots)", y="Sleep (hours)", title="Relationship between Caffeine and Hours of Sleep") +scale_fill_manual(values=c("magenta","cornflowerblue")) +geom_smooth(method="lm", se=TRUE, size=1)
R
```

**Summary and Analysis**
* [Correlation between weak/strong. Linear model shows. Weak correlation for feamles (r=0.18) and males (r=0.19) can likely be explained by...]


### Latest Screen Time on Hours of Sleep?
```{r}
S=ggplot(surveyC, aes(WakeO, Sleep,fill=Screen) +geom_point(size=3, pch=21,aes(col=Screen)) +labs(x="Wakeup Time", y="Sleep (hours)", title="Latest Screen Time on Hours of Sleep") +geom_smooth(method="lm", se=TRUE)

S

```


* Wake (time)/Work (hours) on Hours of Sleep?
```{r}
WakeO=factor(survey$Wake, levels=c("2:00","4:30", "4:45","5:00","5:30","6:00","6:30","6:45","7:00","7:10","7:15","7:20","7:35","8:00","8:30","9:00","9:30","10:00","10:30","11:00","11:30","12:00"))

W=ggplot(surveyC, aes(WakeO, Sleep,fill=Screen)) +geom_col(size=3, pch=1,aes(col=Screen)) +labs(x="Wake up Time", y="Sleep (hours)", title="Relationship between Wake Up Time on Hours of Sleep") +theme(axis.text.x=element_text(angle=90, vjust=0.5, hjust=1))

# Wake-up time or Work (hours) --> Was thinking maybe a Histogram??

W
```



# Articles
[at least 2 articles]

# References
[APA references for the above 2 articles]

# Acknowledgments
**Date & Time**    |    **Present**                    |   **Topic**
-------------------|---------------------------------|------------------
  8/3/22, 5:10PM   |   All present                   | Project 1 (0%)
  29/3/22, 4:35PM  | Hatim, Harshini, Chiara, Norma, | Project 2 (13%) -
                   | (Ravi + Bella exemption reasons)| Data Cleaning Survey A’s
  5/4/22, 5:05PM   |   All (Norma virtually)         | Dividing + Assigning Tasks 
                   |                                 | (2 subgroups)


